---
title: "Predictor Charles Schwab Challenge 2021"
author: ""
date: ""
output:  
  prettydoc::html_pretty:
    theme: lumen
    highlight: github
    runtime: shiny
---

# How does it works?

It takes stats about the 2020 Charles Schwab Challenge and generates a model with the Strokes Gained so an aproxiamte position is given.

## SG: Total

Simply compares a player's score to the field average. For example, a player will gain three strokes on the field if he shoots 69 on a day when the field averages 72. A player who shoots 74 on that day loses two strokes to the field. And here it is divided in SG: Putting, SG: Off-the-tee, SG: Aproach, SG: Around-the-green

# Dataset

```{r, echo = FALSE}
dataset <- read.csv("~/Programacion/R/CharlesSchwab2020/CSC2020Data.csv")
knitr::kable(dataset[1:67,1:9], format="html")
```

# Analisis

Se analizan las variables mas importantes

```{r,echo = FALSE,message = FALSE}
data <- dataset[,-2]
data <- data[,-2]

for(i in 1:7){
  data[, i] <- as.numeric(data[, i])
}

library(corrplot)
corrplot(cor(data), method= 'color')
```

# Predictor




```{r,echo=FALSE,}
ui <- fluidPage(
  sidebarLayout(
    sidebarPanel(
      numericInput("sgputt", "SG: Putting", value = 0,step = 0.1),
      numericInput("sgApp", "SG: Approach", value = 0,step = 0.1),
      numericInput("sgOtt", "SG: Off-The-Tee", value = 0,step = 0.1),
      numericInput("sgArg", "SG: Around-The-Green", value = 0,step = 0.1),
    ),
    mainPanel(
      textOutput("position"),
      tags$head(tags$style("#position{color: black;
                                 font-size: 40px;
                                 font-style: bold;
                                 padding: 80px;
                              
                                 }"
                         )
              )

    )
  )
)

server <- function(input, output, session) {
     output$position = renderText({paste("Expected Position: ",predictor(input$sgputt,input$sgApp,input$sgOtt,input$sgArg))})
}

shinyApp(ui = ui, server = server)

Pos <- data$POSITION
SGTotal <- data$SG.T
SGPutting <- data$SG.P
SGAPR <- data$SG.APR
SGOTT <- data$SG.OTT
SGARG <- data$SG.ARG
model <- lm(SGTotal ~ SGPutting + SGAPR + SGOTT + SGARG)
model2 <- lm(Pos ~ SGTotal)

predictor <- function(putting, approach, offthetee, aroundgreen){
  sgtot <- predict(model, newdata = data.frame(SGPutting = putting, SGAPR = approach, SGOTT = offthetee, SGARG = aroundgreen))
  position <- round(predict(model2, newdata = data.frame(SGTotal = sgtot)))
  if(position < 0){
    return("Too Good")
  }else if(position > 80){
    return("CUT")
  }else{
    return(position)
  }
}

```